SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-18 response.tex

\multirow{4}{*}{\textcolor{blue}{None}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.96} & \textcolor{blue}{0.90} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.10} & \textcolor{blue}{0.95} & \textcolor{blue}{0.92} \\ 
                        & \textcolor{blue}{FLTrust}   & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ 
                        & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.13} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.93} & \textcolor{blue}{0.85} \\ 
                        & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline

\multirow{4}{*}{\textcolor{blue}{Size}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.96} & \textcolor{blue}{0.90} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.10} & \textcolor{blue}{0.95} & \textcolor{blue}{0.92} \\ 
                        & \textcolor{blue}{FLTrust}   & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ 
                        & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.13} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.93} & \textcolor{blue}{0.85} \\ 
                        & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline

\multirow{4}{*}{\textcolor{blue}{Angle}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.96} & \textcolor{blue}{0.90} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.10} & \textcolor{blue}{0.95} & \textcolor{blue}{0.92} \\ 
                        & \textcolor{blue}{FLTrust}   & \textcolor{blue}{0.94} & \textcolor{blue}{0.85} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.15} & \textcolor{blue}{0.93} & \textcolor{blue}{0.88} \\ 
                        & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.13} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.93} & \textcolor{blue}{0.85} \\ 
                        & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline

### 2024-11-18 main-v2.tex
fix: GPT表格填写错误
Signed-off-by: LetMeFly666 <814114971@qq.com>

\begin{table}[h!]
\small
\centering
\caption{\textcolor{red}{Metrics results with different attack and defense methods.}}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{c|c|c|c|c|c|c|c}
\hline

\textcolor{red}{Strategy} & \textcolor{red}{Defense} & \textcolor{red}{Acc.} & \textcolor{red}{Rec.} & \textcolor{red}{FPR} & \textcolor{red}{FNR} & \textcolor{red}{AUC} & \textcolor{red}{MCC} \\ \hline

@@

\multirow{4}{*}{\textcolor{red}{Angle}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.96} & \textcolor{red}{0.90} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.10} & \textcolor{red}{0.95} & \textcolor{red}{0.92} \\ 
                        & \textcolor{red}{FLTrust}   & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ 
                        & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.13} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.93} & \textcolor{red}{0.85} \\ 
                        & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline

>>>>

\begin{table}[h!]
\small
\centering
\caption{\textcolor{red}{Metrics results with different attack and defense methods.}}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{c|c|c|c|c|c|c|c}
\hline
% 0.96, 0.9, 0.0, 0.1, 0.95, 0.9185586535436917
% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
% 0.92, 1.0, 0.13333333333333333, 0.0, 0.9333333333333333, 0.8498365855987975
% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
% ----------------
% 0.96, 0.9, 0.0, 0.1, 0.95, 0.9185586535436917
% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
% 0.92, 1.0, 0.13333333333333333, 0.0, 0.9333333333333333, 0.8498365855987975
% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
% ----------------
% 0.96, 0.9, 0.0, 0.1, 0.95, 0.9185586535436917
% 0.94, 0.85, 0.0, 0.15, 0.925, 0.8790490729915326
% 0.92, 1.0, 0.13333333333333333, 0.0, 0.9333333333333333, 0.8498365855987975
% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
\textcolor{red}{Strategy} & \textcolor{red}{Defense} & \textcolor{red}{Acc.} & \textcolor{red}{Rec.} & \textcolor{red}{FPR} & \textcolor{red}{FNR} & \textcolor{red}{AUC} & \textcolor{red}{MCC} \\ \hline

@@

\multirow{4}{*}{\textcolor{red}{Angle}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.96} & \textcolor{red}{0.90} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.10} & \textcolor{red}{0.95} & \textcolor{red}{0.92} \\ 
                        & \textcolor{red}{FLTrust}   & \textcolor{red}{0.94} & \textcolor{red}{0.85} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.15} & \textcolor{red}{0.93} & \textcolor{red}{0.88} \\ 
                        & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.13} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.93} & \textcolor{red}{0.85} \\ 
                        & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline
